---
format:
  dashboard:
    orientation: rows
project:
  output-dir: docs/
---

```{r}
library(htmltools)
```

```{r}
TheDate <- Sys.Date()
```

## {.sidebar}
Dashboard contains historical data for the **Cytek Aurora CS**.

**Contents:**

**Interactive** A redirect to the interactive Levey-Jennings plots for the respective year.

**Plots** A .pdf file containing non-interactive version of all the plots for the respective year.

**Gain and MFI** A .csv file containing Gain and MFI information derrived from Daily QC .fcs files used to generate the plots.

For additional information, navigate to the [Help](https://umgccfcss.github.io/InstrumentQC/help) page.

**About**

This dashboard contains the visualized QC data for the Cytek and BD cytometers at the [UMGCC FCSS](https://www.medschool.umaryland.edu/cibr/core/umgccc_flow/)

For additional flow cytometry resources, visit our [website](https://sites.google.com/view/umgcccflow/home)

This dashboard was created with [Quarto](https://quarto.org/) and is maintained by [David Rach](https://github.com/DavidRach)


## First Row {height="50%"}

### Year 2023 {width="50%"}

::: {.card title="" width="33%"}

:::

```{r}
#| content: valuebox
#| title: "Year 2023"
#| icon: cup-hot

HTML("
<ul>
  <li><a href='Year2023.html'>Interactive</a></li>
  <li><a href='data/Historical_AuroraCS_2023.pdf'>Plots</a></li>
  <li><a href='data/Historical_AuroraCS_2023.csv'>Gain and MFI</a></li>
</ul>
")
```

### Current {width="50%"}

::: {.card title="" width="33%"}

:::

```{r}
#| content: valuebox
#| title: "Current"
#| icon: cup-hot

HTML("
<ul>
  <li><a href='https://umgccfcss.github.io/InstrumentQC/AuroraCS'>Interactive</a></li>
  <li><a href='https://umgccfcss.github.io/InstrumentQC/data/QCPlots_CS.pdf'>Plots</a></li>
  <li><a href='https://umgccfcss.github.io/InstrumentQC/data/CS/Archive/BeadDataCS.csv'>Gain and MFI</a></li>
</ul>
")
```

## Second Row {height="50%"}

### Year 2024 {width="50%"}

```{r}
#| content: valuebox
#| title: "Year 2024"
#| icon: cup-hot

HTML("
<ul>
  <li><a href='Year2024.html'>Interactive</a></li>
  <li><a href='data/Historical_AuroraCS_2024.pdf'>Plots</a></li>
  <li><a href='data/Historical_AuroraCS_2024.csv'>Gain and MFI</a></li>
</ul>
")
```

::: {.card title="" width="33%"}

:::


### Extra {width="50%"}

```{r}
#| content: valuebox
#| title: "Extra"
#| icon: cup-hot

HTML("
<ul>
  <li><a href='https://umgccfcss.github.io/InstrumentQC/AuroraCS'>Interactive</a></li>
  <li><a href='https://umgccfcss.github.io/InstrumentQC/data/QCPlots_CS.pdf'>Plots</a></li>
  <li><a href='https://umgccfcss.github.io/InstrumentQC/data/CS/Archive/BeadDataCS.csv'>Gain and MFI</a></li>
</ul>
")

```

::: {.card title="" width="33%"}

:::
 


